\documentclass[11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preamble:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Typical Packages:
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{empheq}
\usepackage{mathrsfs}
\usepackage{enumerate}
\usepackage{tikz}
\usepackage{upgreek}
\usepackage{tipa}
\usepackage{multicol}
\usepackage{verbatim}
\usepackage{floatrow}
\usepackage{gensymb}
\usepackage{caption}
\usepackage[T1]{fontenc}
\usepackage[font=small,labelfont=bf,tableposition=top]{caption}

\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Start Document:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% Title: 
\begin{center}
\Large{\textsc{Post-Course Survey }}\\
\end{center}

\vspace{.2cm}

% Survey Questions:
\begin{enumerate}[{$\qquad 1.]$}]

\item What is your name?\vfill

%\item What is the highest level math course you've taken so far at KU? \vfill

\item On a scale of 1-5, how confident do you feel about using Python for programming tasks? How would you rate your overall proficiency in Python? (Beginner, Intermediate, Advanced) \vfill

\item What specific areas of Python do you feel most confident in, and where do you feel you need more practice? \vfill


\item How do you rate your ability to break down a problem into smaller, manageable parts and implement a solution in Python?\vfill


\item On a scale of 1-5, how confident are you in using \LaTeX\, for document preparation?  How would you rate your overall proficiency in \LaTeX? (Beginner, Intermediate, Advanced) \vfill

\item How confident are you in creating a multi-page report or academic paper in \LaTeX, including sections, subsections, and references? \vfill

\item How comfortable are you with using and modifying \LaTeX\, templates (e.g., for resumes, presentations, or reports)? \vfill


%\item Next to each mathematical software listed below, write down a number between 0 and 10 that represents your competence with that program.  ``0'' means you've never used it before and ``10'' means you are very comfortable using it or are proficient in it.''
%\begin{itemize}
%	\item Mathematica $\line(1,0){40}$
%	\item SageMath $\line(1,0){40}$
%	\item Python $\line(1,0){40}$
%	\item Matlab $\line(1,0){40}$
%	\item Excel $\line(1,0){40}$
%	\item Minitab $\line(1,0){40}$
%	\item \LaTeX~$\line(1,0){40}$
%\end{itemize}

%\item Rank the projects in order of your preference.  ``1'' is your favorite project and ``5'' is your least favorite project.  
%\begin{itemize}
%	\item Project 1 -- Optimal Billing Strategy $\line(1,0){40}$
%	\item Project 2 -- Predicting Beer Sales $\line(1,0){40}$
%	\item Project 3 -- Manpower Allocation $\line(1,0){40}$
%	\item Project 4 -- Optimal Delivery Route $\line(1,0){40}$
%	\item Project 5 -- Inflow and Infiltration $\line(1,0){40}$
%\end{itemize}

\item How did the course structure (lectures, assignments, projects) help you learn Python effectively?\vfill


\item What could have been done differently in the course to improve your understanding of Python and \LaTeX?\vfill

\item How do you plan to use Python in your future academic or professional work?


%\item List any other programs that you have used other than Python that you could potentially use for this class. \vfill

%\item What do you expect to get out of this class? \vfill

\end{enumerate}

\end{document}