\documentclass[article, 11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preamble:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Typical Packages:
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{palatino, url, multicol}
\usepackage{enumerate}
\usepackage{ulem}
\usepackage{hyperref}
\usepackage{verbatim}

\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Start Document:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% Project Title:
\begin{center}\boxed{\LARGE{\textbf{\textsc{ MINI-PROJECT 3}}}}\\
\Huge{\textbf{\textsc{ Modeling with ODEs}}} \\ \end{center}

\vspace{.6cm}

% Brief Summary:
\noindent \boxed{\textbf{\textsc{Brief Summary}}}

\vspace{-.35cm}
\noindent \hrulefill

In this project, you will explore the numerical methods for solving ordinary differential equations (ODEs) in Python, focusing on one-dimensional ODEs and systems of ODEs. ODEs are vital in modeling a variety of real-world phenomena, including population dynamics, aerospace applications, infectious diseases, mechanical systems, pharmaco-kinetics, chemical reactions, and electrical circuits. This project will provide hands-on experience in implementing solutions using Python’s scientific libraries, with an emphasis on both theoretical understanding and practical applications.  \\ 


% Goals:
\noindent \boxed{\textbf{\textsc{Goals}}}

\vspace{-.35cm}
\noindent \hrulefill

\begin{itemize}
\item Develop a deep understanding of numerical methods used to solve ODEs, such as Euler’s Method and Runge-Kutta methods.
\item Apply Python libraries like \text{scipy} to solve and analyze one-dimensional ODEs and systems of ODEs.
\item Explore real-world applications of ODEs in physics, biology, and engineering.
\item Visualize the solutions and interpret their behavior in the context of the application.
\end{itemize}

% Where to Start: 
\noindent \boxed{\textbf{\textsc{Where to Start}}}

\vspace{-.35cm}
\noindent \hrulefill

We'll start by looking at basic commands in Python to solve one-dimensional ODEs and then move onto larger systems of nonlinear ODEs. We'll formulate linear and nonlinear equations with motivation from biology and physics.  Some equations we'll solve by hand and compare the analytical solution to the numerical solution given by Python.  We'll then work into more sophisticated ODE systems and explore wider reaching applications.   \\

% Skills Needed/Gained:
\noindent \boxed{\textbf{\textsc{Skills Needed/Gained:}}}

\vspace{-.35cm}
\noindent \hrulefill

\begin{itemize}
	\item Formulating linear and nonlinear ODEs and systems of ODEs.  
	\item Visualizing the effects of parameter variation on model output.
	\item Fitting ODE models to data. 
	\item Document creation in \LaTeX. 
\end{itemize}

\noindent \hrulefill

\end{document}